---
title: "did_example"
author: "Qinlu.Hu"
date: "`2022/11/1`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(did)
```

# An example with real data

## (1) import a subset of data that comes from Callaway and Sant’Anna (2020)

```{r}
data(mpdta)
```

## This is a dataset that contains county-level teen employment rates from 2003-2007. 
### Y= lemp

```{r}
head(mpdta)
```

## (2) The Effect of the Minimum Wage on Youth Employment

### group-time average treatment effects

```{r}
# estimate group-time average treatment effects without covariates
mw.attgt <- att_gt(yname = "lemp",
                   gname = "first.treat",
                   idname = "countyreal",
                   tname = "year",
                   xformla = ~1,
                   data = mpdta,
                   )
```

```{r}
summary(mw.attgt)
```

### plot the results
```{r}
ggdid(mw.attgt, ylim = c(-.3,.3))
```

### aggregate the group-time average treatment effects
```{r}
mw.dyn <- aggte(mw.attgt, type = "dynamic")
summary(mw.dyn)
```

### plot
```{r}
ggdid(mw.dyn, ylim = c(-.3,.3))
```

### run all the same results including a covariate

```{r}
mw.attgt.X <- att_gt(yname = "lemp",
                   gname = "first.treat",
                   idname = "countyreal",
                   tname = "year",
                   xformla = ~lpop,
                   data = mpdta,
                   )
```

