---
title: "did_demo"
author: "Qinlu.Hu"
date: "`2022/11/1`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Callaway and Sant’Anna (2020) 
library(did)
```

# A simulation demo

## (1) create simulation data
```{r}
time.periods <- 4
sp <- reset.sim()
sp$te <- 0     #create blank dataframe
```

```{r}
# set seed so everything is reproducible
set.seed(1814)

# generate dataset with 4 time periods
time.periods <- 4

# add dynamic effects
sp$te.e <- 1:time.periods

# generate data set with these parameters
# here, we dropped all units who are treated in time period 1 as they do not help us recover ATT(g,t)'s.
dta <- build_sim_dataset(sp)

# How many observations remained after dropping the ``always-treated'' units
nrow(dta)
#This is what the data looks like
head(dta)
```

## (2) Estimating Group-Time Average Treatment Effects

```{r}
example_attgt <- att_gt(yname = "Y",
                        tname = "period",
                        idname = "id",
                        gname = "G",
                        xformla = ~X,
                        data = dta
                        )

```

```{r}
summary(example_attgt)
```

## (3) plot group-time average treatment effects
```{r}
ggdid(example_attgt)
```

## (4) Aggregating group-time average treatment effects

### Method 1: Simple Aggregation (a weighted average of all group-time average treatment effects with weights proportional to the group size.  This is available by calling the `aggte` function with `type = simple`)
```{r}
agg.simple <- aggte(example_attgt, type = "simple")
summary(agg.simple)
```

### Method 2: Dynamic Effects and Event Studies( aggregate group-time effects into an event study plot)

```{r}
agg.es <- aggte(example_attgt, type = "dynamic")
summary(agg.es)
ggdid(agg.es)
```

### Method 3:Group-Specific Effects(average effects specific to each group)

```{r}
agg.gs <- aggte(example_attgt, type = "group")
summary(agg.gs)
ggdid(agg.gs)
```

### Method 4: Calendar Time Effects(aggregations across different time periods)

```{r}
agg.ct <- aggte(example_attgt, type = "calendar")
summary(agg.ct)
ggdid(agg.ct)
```
## (5) other options

### chose control group
```{r}
# By default, the did package uses the group of units that never participate in the treatment as the control group.
#  The other option for the control group is to use the “not yet treated”

example_attgt_altcontrol <- att_gt(yname = "Y",
                                   tname = "period",
                                   idname = "id",
                                   gname = "G",
                                   xformla = ~X,
                                   data = dta,
                                   control_group = "notyettreated"          
                                   )
summary(example_attgt_altcontrol)
```

### choose estimation method

```{r}
# By default, the did package uses “doubly robust” estimators 
# The other options are “ipw” for inverse probability weighting and “reg” # for regression
example_attgt_reg <- att_gt(yname = "Y",
                            tname = "period",
                            idname = "id",
                            gname = "G",
                            xformla = ~X,
                            data = dta,
                            est_method = "reg"
                            )
summary(example_attgt_reg)

```

